Structured Versus Decorated Cospans

### 2020-11-11 cospans.tex
small preamble edits, also changed geometry, fill free to amend
the issue was in fact already resolved

\documentclass{amsart}
\input{Equiv_preamble.tex}
\usepackage[foot]{amsaddr}

@@

\setcounter{tocdepth}{1} % comment this out if you want to see the subsections in the table of contents
\tableofcontents

\section*{Various issues-in-progress}

\begin{itemize}
\item {\chris Notation between \cref{Equiv} and \cref{thm:decoratedcospans} right now does not match! Need to fix. Slightly prefer a,b,c for objects of A, then $a'$ and $b'$ for other objects, and x an object of the category F(c) namely the decoration. The previously used `d' is slightly confusing around all these a's, b's and c's that are in a different category. Also I prefer $a$ and $b$ rather than $a_1$ and $a_2$.}

{\chris After a brief discussion in John's office, for \cref{Equiv} I used $a,b,c$ for the feet and $m,n$ for the apices so we can serially compose. Of course can change as we like.}
%\item {\chris There might be a way to completely hide the details of version 'fibres have, reindexing preserve' if that's what we want to do.}

\end{itemize}

>>>>

\documentclass{amsart}
\input{Equiv_preamble.tex}

@@

\setcounter{tocdepth}{1}
\tableofcontents
